### 2015-02-20 sicp/Cohort 1/chapter-1.2/ndpar-1.2.tex
Just doing a bit of housekeeping here
I don't think this lost anything but some of the deletions are a
little concerning because they should have a corresponding creation.

\documentclass[12pt]{article}

\usepackage{amsthm}
\usepackage{amsmath}    % need for subequations
\usepackage{amsfonts}
\usepackage[ocgcolorlinks]{hyperref}

\setlength{\baselineskip}{16.0pt}    % 16 pt usual spacing between lines

\setlength{\parskip}{3pt plus 2pt}
\setlength{\parindent}{20pt}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}
\setlength{\marginparsep}{0.75cm}
\setlength{\marginparwidth}{2.0cm}
\setlength{\marginparpush}{1.0cm}
\setlength{\textwidth}{150mm}

\DeclareMathOperator{\sinc}{sinc}
\DeclareMathOperator{\sgn}{sgn}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\begin{document}

\section{Example: Counting change}

\begin{lemma}
    $\forall n, d, k \in \mathbb{N} : d, k \ge 1 \implies n^{k-1} + (n-d)^k \le n^k$
\end{lemma}

\begin{proof}
    $$d \ge 1 \implies n - d \le n - 1 < n.$$
    $$k \ge 1 \implies (n-d)^{k-1} < n^{k-1}.$$
    $$(n-d)^k = (n-d)(n-d)^{k-1} \le (n-1)n^{k-1} = n^k - n^{k-1}.$$
\end{proof}

\begin{definition}
    $T(n,k)$ is the number of ways to change amount $n$ using $k$ kinds of coins. $n, k \in \mathbb{N}, n, k \ge 1$.
\end{definition}

\begin{theorem}
    $T(n,k) = O(n^k).$
\end{theorem}

\begin{proof}
    To prove the theorem we have to show that $\exists c>0$ such that $T(n,k) \le cn^k$ for sufficiently large $n$.
    Let's prove it using substitution method (CLRS, p.83).

    Assume that the inequality is true.
    The recurrence formula for $T(n,k)$ is
    $$T(n,k) = T(n,k-1) + T(n-d,k),$$
    where $d$ is denomination of the first coin. $d \ge 1$. Therefore by Lemma
    $$T(n,k) \le cn^{k-1} + c(n-d)^k = c\left[n^{k-1} + (n-d)^k\right] \le cn^k.$$

    To finish the proof, we just need to find $c$. Since the boundary condition $T(1,1) = 1$, it's sufficient to put $c \ge 1$.
\end{proof}

\end{document}

### 2015-11-13 pfpl/cheatsheet.tex
Beginning of cheatsheet

\documentclass{article}

\usepackage{default}
\newcommand{\s}[1]{\parbox{7em}{#1}}
\newcommand{\m}[1]{\parbox{23em}{#1}}

\begin{document}
\begin{tabular}[b] {l l l l}
Expression & Name & Say & Meaning \\ \\
$\mathcal{P}$ & Script P & \s{Proposition} & \m{Something to be proved} \\
$\mathcal{P}(\it{a})$ & Script P sub a & \s{Proposition about tree $\it{a}$} & \m{Something to be proved about abstract syntax tree $\it{a}$}
\end{tabular}

\end{document}

### 2015-11-26 pfpl/cheatsheet.tex
Put concept sort into cheat sheet.

@@
-\documentclass{article}
+\documentclass[12pt]{article}
+\usepackage[margin=.5in]{geometry}
+\begin{document}
+\begin{tabular}[b] {p{.1\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
+Expression & Name & Say & Meaning \\ \\
+$\mathcal{P}$ & Script P & Proposition & Something to be proved \\
+$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$
 
-\usepackage{default}
-\newcommand{\s}[1]{\parbox{7em}{#1}}
-\newcommand{\m}[1]{\parbox{23em}{#1}}
-
-\begin{document}
-\begin{tabular}[b] {l l l l}
-Expression & Name & Say & Meaning \\ \\
-$\mathcal{P}$ & Script P & \s{Proposition} & \m{Something to be proved} \\
-$\mathcal{P}(\it{a})$ & Script P sub a & \s{Proposition about tree $\it{a}$} & \m{Something to be proved about abstract syntax tree $\it{a}$}
 \end{tabular}

### 2015-11-26 pfpl/cheatsheet.tex
Add new files Add .gitignore Create sort branch
Remove sort
First cut at some contents to see if this is the right direction.

@@
 \documentclass[12pt]{article}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{proof}
+\usepackage{hyperref}
+
 \usepackage[margin=.5in]{geometry}
@@
 $\mathcal{P}$ & Script P & Proposition & Something to be proved \\
-$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$
+$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$ \\
+$\mathcal{O}$ & Script O & Operator & An operator that can be used in an AST \\
+$\mathcal{O}(\it{a})$ & Script O of $\it{a}$ & Operator of arity $\it{a}$ & An operator of a given arity \\
+$\mathcal{X}_{\it{s}}$ & Script X sub s & Variable $\it{x}$ of sort $\it{s}$ & A variable x of sort s \\
+$\{ X _{s} \} _{\it{s} \in \mathcal{S}}$  & Family & Set X of s & a sort-indexed family of disjoint finite sets X s of variables x of sort s
 

### 2015-11-27 pfpl/cheatsheet.tex
First draft of chapter 1

--- 2015-11-26 pfpl/cheatsheet.tex
@@
 \documentclass[12pt]{article}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{proof}
+\usepackage{hyperref}
+
 \usepackage[margin=.5in]{geometry}
 \begin{document}
-\begin{tabular}[b] {p{.1\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
+\section*{Chapter 1}
+\begin{tabular}[b] {p{.15\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
 Expression & Name & Say & Meaning \\ \\
 $\mathcal{P}$ & Script P & Proposition & Something to be proved \\
-$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$
-
+$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$ \\
+$\mathcal{O}$ & Script O & Operator & An operator that can be used in an AST \\
+$\mathcal{O}(\it{a})$ & Script O of $\it{a}$ & Operator of arity $\it{a}$ & An operator of a given arity \\
+$\mathcal{X}_{\it{s}}$ & Script X sub s & Variable $\it{x}$ of sort $\it{s}$ & A variable $\it{x}$ of sort $\it{s}$ \\
+$\{ \it{X}_{s} \} _{\it{s} \in \mathcal{S}}$  & Family & Set $ \it{X} $ of s & a sort-indexed family of disjoint finite sets $ \it{X}_s $ of variables $\it{x}$ of sort $ \it{s} $ \\
+$\left[ \it{b} / \it{x}\right] \it{a}$ & Substitution & Substitute $\it{b}$ for $\it{x}$ in $\it{a}$ & Substitute $\it{b}$ for $\it{x}$ in $\it{a}$ \\
+$ \it{x}_1, ... ,\it{x}_{\it{n}}.\it{a} $ & Abstractor & Bind variables $\it{x_n}$ to expression $\it{a}$ & Bind variables $\it{x_n}$ to expression $\it{a}$ \\
+$ \overrightarrow{\it{x}} $ & X arrow & List of $\it{x}s$ & $ \it{x}_1, ... ,\it{x}_{\it{n}} $ \\
+$ \rho : \overrightarrow{\it{x}} \leftrightarrow \overrightarrow{\it{x}}'$ & Fresh renaming & Freshen $ \it{x} $ in $ \it{a} $ renaming & A bijection between $ \overrightarrow{\it{x}} $ and $ \overrightarrow{\it{x}}' $ where $ \overrightarrow{\it{x}}'$ is fresh for $\it{X}$ .
+\\
+$\widehat{\rho}_i (a_i)$ & Rho hat sub i & Rename result & The result of applying the renaming $ \rho $ to $ \it{a} $ \\
+$ =_\alpha $ & Equal alpha & $ \it{\alpha-equivalence} $ & Equal trees up to renaming \\
+$ \overset{\Delta}{=} $ & & & \\
 \end{tabular}

### 2015-12-04 pfpl/cheatsheet.tex
Edited version of chapter 1

--- 2015-11-26 pfpl/cheatsheet.tex
@@
 \documentclass[12pt]{article}
-\usepackage[margin=.5in]{geometry}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{proof}
+\usepackage{hyperref}
+
+\usepackage[margin=.25in]{geometry}
 \begin{document}
-\begin{tabular}[b] {p{.1\textwidth} p{.15\textwidth} p{.22\textwidth} p{.4\textwidth}}
-Expression & Name & Say & Meaning \\ \\
-$\mathcal{P}$ & Script P & Proposition & Something to be proved \\
-$\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about abstract syntax tree $\it{a}$
-
+\begin{tabular}[b] {p{.05\textwidth} p{.13\textwidth} p{.15\textwidth} p{.22\textwidth} p{.32\textwidth}}
+Page & Expression & Name & Say & Meaning \\ \\
+5& $\mathcal{P}$ & Script P & Proposition & Something to be proved \\
+5& $\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about AST $\it{a}$ \\
+5& $\mathcal{O}$ & Script O & Operator & An operator that can be used in an AST \\
+5& $\mathcal{O}(\it{a})$ & Script O of $\it{a}$ & Operator of arity $\it{a}$ & An operator of a given arity \\
+5& $\mathcal{X}_{\it{s}}$ & Script X sub s & Variables $\it{x}$ of sort $\it{s}$ & Variables $\it{x}$ of sort $\it{s}$ \\
+5& $\it{S} $ & S & A set of sorts & A set of sorts \\
+5& $ \{ \it{X}_{s} \} _{\it{s} \in \mathcal{S}}$  & Family & Family $ \it{X} $ of $\it{s}$ & a sort-indexed family of disjoint finite sets $ \it{X}_s $ of variables $\it{x}$ of sort $ \it{s} $\\
+6& $\left[ \it{b} / \it{x}\right] \it{a}$ & Substitution & Substitute $\it{b}$ for $\it{x}$ in $\it{a}$ & Substitute  $\it{b}$ for $\it{x}$ in $\it{a}$ \\
+7& $ \it{x}_1, ... ,\it{x}_{\it{n}}.\it{a} $ & Abstractor & Bind variables $\it{x_n}$ to expression $\it{a}$ & Bind variables $\it{x_n}$ to expression $\it{a}$ \\
+8& $ \overrightarrow{\it{x}} $ & X arrow & List of $\it{x}s$ & $ \it{x}_1, ... ,\it{x}_{\it{n}} $ \\
+8& $ \rho : \overrightarrow{\it{x}} \leftrightarrow \overrightarrow{\it{x}}'$ & Fresh renaming & Freshen $ \it{x} $ using renaming $ \rho $ & A bijection between $ \overrightarrow{\it{x}} $ and $ \overrightarrow{\it{x}}' $ where $ \overrightarrow{\it{x}}'$ is fresh.
+\\
+8& $\widehat{\rho}_{\it{i}} (a_{\it{i}})$ & Rho hat sub i & Rename result & The result of applying the renaming $ \rho_ {\it{i}} $ to $ \it{a}_{\it{i}} $ \\
+8& $x =_\alpha y$ & Equal alpha & $ \it{\alpha}$-$\it{equivalence} $ & Trees x and y equal up to renaming \\
+9& $x \overset{\Delta}{=} y$ & Delta equals & Definitially equals & Trees x and y are definitionally equal \\
 \end{tabular}

### 2016-01-29 pfpl/cheatsheet.tex
Add Chapter 2

@@
 9& $x \overset{\Delta}{=} y$ & Delta equals & Definitially equals & Trees x and y are definitionally equal \\
+13& $\tau$ type& type & type $\tau$ & Judgement that $\tau$ is a type \\
+13& $\it{e} : \tau$ & expression type & expression $\it{e}$ is of type $\tau$ & Judgement that expression $\it{e}$ is of type $\tau$ \\
+13& $\it{e} \Downarrow \it{v}$ & expression value & expression $\it{e}$ has value $\it{v} $ & Judgement that expression $\it{e}$ has value $\it{v} $\\
+14& $\infer {\it{J}} {\it{J}_{1}...\it{J}_{\it{k}}}$  & surfboard & infers & Judgements ${\it{J}_{1}...\it{J}_{\it{k}}}$ infer judgement ${\it{J}}$\\
+
 \end{tabular}

### 2016-02-06 pfpl/cheatsheet.tex
Added more definitions to cheatsheet.  Started staying current.

--- 2015-12-04 pfpl/cheatsheet.tex
@@
 8& $x =_\alpha y$ & Equal alpha & $ \it{\alpha}$-$\it{equivalence} $ & Trees x and y equal up to renaming \\
-9& $x \overset{\Delta}{=} y$ & Delta equals & Definitially equals & Trees x and y are definitionally equal \\
+9& $x \overset{\Delta}{=} y$ & Delta equals & Replacement & Replace expression x with expression y \\
+13& $\tau$ type& Type & Type $\tau$ & Judgement that $\tau$ is a type \\
+13& $\it{e} : \tau$ & Colon &  $\it{e}$ is of type $\tau$ & Judgement that expression $\it{e}$ is of type $\tau$ \\
+13& $\it{e} \Downarrow \it{v}$ & Down arrow &  $\it{e}$ has value $\it{v} $ & Judgement that expression $\it{e}$ has value $\it{v} $\\
+14& $\infer {\it{J}} {\it{J}_{1}...\it{J}_{\it{k}}}$  & Surfboard & Infers & Judgements ${\it{J}_{1}...\it{J}_{\it{k}}}$ infer judgement ${\it{J}}$\\
+23 & ${\it{J}_{1}...\it{J}_{\it{k}}} \vdash_{\mathcal{R}} \mathcal{K}$ & Turnstile & Entails & Given $\mathcal{R}$ and $\it{J}$ infer $\mathcal{K}$\\
+23 & $\Gamma$ & Gamma & Judgements Gamma & A finite set of judgements \\
+23 & $\Delta$ & Delta & Judgements Delta & A finite set of judgements \\
+25 & $\Gamma \models_{\it{R}} \it{J}$ & Double turnstile & Admissible & $\vdash_{\it{R}} \Gamma$ implies $\vdash_{\it{R}} \it{J}$ \\
+28 & $\bigtriangledown$ & Down triangle & Generic derivation & Generic derivation \\
+41 & $\it{s} \mapsto \it{s'}$ & Bar arrow & Transistion  & State $\it{s}$ transitions to state $\it{s'}$ \\
+
+42 & $\it{s} \mapsto ^{*} \it{s'}$ & Bar arrow star & Iterated transistion  & State $\it{s}$ transitions to state $\it{s'}$ over more than zero transitions \\
+
+42 & $\it{s} \mapsto ^{n} \it{s'}$ & Bar arrow n & N times iterated transistion  & State $\it{s}$ transitions to state $\it{s'}$ over n transitions \\
+
+44 & $\mathcal{E}$  & Script E & Expression context & Expression context \\
+
+45 & $\circ $ & Circle & Hole & Placeholder to put an instruction \\
+46 & $ \it{e} \equiv \it{e}' $ & Equivalent & Definitional equivalence & $\it{e}$ is definitionally equivalent to $\it{e}'$ \\
+
+58 & $\it{e}??$ & Wrong & E goes wrong & Expression $\it{e}$ goes wrong \\
+
+58 & $\it{e} \Downarrow ^{\it{k}}\it{v}$  & Downarrow k & E evaluates in k steps & Expression $ \it{e}$ evaluates to $\it{v}$ in $\it{k}$ steps\\
+
+166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
 \end{tabular}

### 2016-02-20 pfpl/cheatsheet.tex

--- 2015-12-04 pfpl/cheatsheet.tex
@@
 \begin{document}
+\section*{Cheat Sheet}
 \begin{tabular}[b] {p{.05\textwidth} p{.13\textwidth} p{.15\textwidth} p{.22\textwidth} p{.32\textwidth}}
@@
 8& $x =_\alpha y$ & Equal alpha & $ \it{\alpha}$-$\it{equivalence} $ & Trees x and y equal up to renaming \\
-9& $x \overset{\Delta}{=} y$ & Delta equals & Definitially equals & Trees x and y are definitionally equal \\
+9& $x \overset{\Delta}{=} y$ & Delta equals & Replacement & Replace expression x with expression y \\
+13& $\tau$ type& Type & Type $\tau$ & Judgement that $\tau$ is a type \\
+13& $\it{e} : \tau$ & Colon &  $\it{e}$ is of type $\tau$ & Judgement that expression $\it{e}$ is of type $\tau$ \\
+13& $\it{e} \Downarrow \it{v}$ & Down arrow &  $\it{e}$ has value $\it{v} $ & Judgement that expression $\it{e}$ has value $\it{v} $\\
+14& $\infer {\it{J}} {\it{J}_{1}...\it{J}_{\it{k}}}$  & Surfboard & Infers & Judgements ${\it{J}_{1}...\it{J}_{\it{k}}}$ infer judgement ${\it{J}}$\\
+23 & ${\it{J}_{1}...\it{J}_{\it{k}}} \vdash_{\mathcal{R}} \mathcal{K}$ & Turnstile & Entails & Given $\mathcal{R}$ and $\it{J}$ infer $\mathcal{K}$\\
+23 & $\Gamma$ & Gamma & Judgements Gamma & A finite set of judgements \\
+23 & $\Delta$ & Delta & Judgements Delta & A finite set of judgements \\
+25 & $\Gamma \models_{\it{R}} \it{J}$ & Double turnstile & Admissible & $\vdash_{\it{R}} \Gamma$ implies $\vdash_{\it{R}} \it{J}$ \\
+28 & $\bigtriangledown$ & Down triangle & Generic derivation & Generic derivation \\
+36 & $ \it{n} ::= \it{s} $ & Colon colon equals & The syntax of $\it{n}$ is $\it{s}$ & Specifies the syntax of $\it{n}$ \\
+36 & $;$ & Semicolon & And & Separates arguments to expressionsin abstact notation\\
+
+41 & $\it{s} \longmapsto \it{s'}$ & Bar arrow & Transistion  & State $\it{s}$ transitions to state $\it{s'}$ \\
+
+42 & $\it{s} \longmapsto ^{*} \it{s'}$ & Bar arrow star & Iterated transistion  & State $\it{s}$ transitions to state $\it{s'}$ over more than zero transitions \\
+
+42 & $\it{s} \longmapsto ^{n} \it{s'}$ & Bar arrow n & N times iterated transistion  & State $\it{s}$ transitions to state $\it{s'}$ over n transitions \\
+
+44 & $\mathcal{E}$  & Script E & Expression context & Expression context \\
+
+45 & $\circ $ & Circle & Hole & Placeholder to put an instruction \\
+46 & $ \it{e} \equiv \it{e}' $ & Equivalent & Definitional equivalence & $\it{e}$ is definitionally equivalent to $\it{e}'$ \\
+
+58 & $\it{e}??$ & Wrong & E goes wrong & Expression $\it{e}$ goes wrong \\
+
+\end{tabular}
+\newpage
+
+\begin{tabular}[b] {p{.05\textwidth} p{.13\textwidth} p{.15\textwidth} p{.22\textwidth} p{.32\textwidth}}
+Page & Expression & Name & Say & Meaning \\ \\
+
+58 & $\it{e} \Downarrow ^{\it{k}}\it{v}$  & Downarrow k & E evaluates in k steps & Expression $ \it{e}$ evaluates to $\it{v}$ in $\it{k}$ steps\\
+
+63 & $\{\it{f}\}$ & Brace brackets & Function & Surround function $\it{f}$ in abstract notation \\
+
+63 & $\it{f}.\it{e}$ & Dot & Dot & Introduces the scope $\it{e}$ of a function $\it{f}$ in abstract notation \\
+64 & $\it{f}(\tau_1):\tau_2$ & Function & Function definition & A function taking an argument of type $\tau_1$ and returning a value of type $\tau_2$ \\
+
+64 & $\mathcal{|[}\it{x/e/f}\mathcal{]|}\it{e'}$ & Script bracket & Function substitution & Function substitution \\
+
+65 & $\tau_1 \to \tau_2$ & Right arrow & Maps to & A total function that maps elements of type $\tau_1$ to elements of type $\tau_2$ \\
+65 & $\lambda $ & Lambda & Lambda & Abstraction \\
+71 & $\hookrightarrow$ & Hook arrow & If & Choice selector \\
+71 & $|$ & Bar & Either & A choice \\
+71 & $\overline{\it{n}}$ & Overline & Succession & The the succession expression corresponding to the number n \\
+76 & $\lceil n \rceil$ & Divided hat & G$\ddot{o}$del numbering & G$\ddot{o}$del numbering \\
+
+166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
+166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
+167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
+175 & $ \simeq $ & Tilde equal & Isomorphism & Isomorphism \\
+177 & $\_$ & Underscore & Underscore & Unfree variable \\
+
 \end{tabular}

### 2016-03-04 pfpl/cheatsheet.tex
Caught up to where we are, modulo some questions.

@@
 23 & $\Gamma$ & Gamma & Judgements Gamma & A finite set of judgements \\
-23 & $\Delta$ & Delta & Judgements Delta & A finite set of judgements \\
+23 & $\Delta$ & Delta & Judgements Delta & A finite set of type judgements \\
 25 & $\Gamma \models_{\it{R}} \it{J}$ & Double turnstile & Admissible & $\vdash_{\it{R}} \Gamma$ implies $\vdash_{\it{R}} \it{J}$ \\
@@
 65 & $\lambda $ & Lambda & Lambda & Abstraction \\
-71 & $\hookrightarrow$ & Hook arrow & If & Choice selector \\
+71 & $\hookrightarrow$ & Hook arrow & Select & Deconstructor selector \\
 71 & $|$ & Bar & Either & A choice \\
@@
 
+81 & $<>$ & Angle brackets & Null tuple & Null tuple \\
+81 & $<e_1,e_2>$ & Angle brackets & Ordered pair & Ordered pair \\
+81 & $e.$l & Left & Left projection & Select left member of the ordered pair \\
+81 & $e.$r & Right & Right projection & Select right member of the ordered pair \\
+
+121 & $t.\tau$ & Dot & Type operator & Bind $t$ to type $\tau$ \\
+133 & $ \cong $ & Tilde equal & Isomorphism & Isomorphism \\
+157 & $::$ & Colon colon & Kind type constructor & Maps types to types \\
 166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
@@
 167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
-175 & $ \simeq $ & Tilde equal & Isomorphism & Isomorphism \\
 177 & $\_$ & Underscore & Underscore & Unfree variable \\
+185 & $\Lambda$ & Lambda & Lambda calculus & The lambda calculus \\
+188 & Y & Y & Y Combinator & The Y combinator \\
+190 & $x^{\dagger}$ & Superscript cross & Superscript cross & Language isomorphism \\
 

### 2016-03-09 pfpl/cheatsheet.tex
Restructured cheatsheet Added new symbols

--- 2016-02-06 pfpl/cheatsheet.tex
@@
 \begin{document}
-\begin{tabular}[b] {p{.05\textwidth} p{.13\textwidth} p{.15\textwidth} p{.22\textwidth} p{.32\textwidth}}
-Page & Expression & Name & Say & Meaning \\ \\
-5& $\mathcal{P}$ & Script P & Proposition & Something to be proved \\
-5& $\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about AST $\it{a}$ \\
-5& $\mathcal{O}$ & Script O & Operator & An operator that can be used in an AST \\
-5& $\mathcal{O}(\it{a})$ & Script O of $\it{a}$ & Operator of arity $\it{a}$ & An operator of a given arity \\
-5& $\mathcal{X}_{\it{s}}$ & Script X sub s & Variables $\it{x}$ of sort $\it{s}$ & Variables $\it{x}$ of sort $\it{s}$ \\
-5& $\it{S} $ & S & A set of sorts & A set of sorts \\
-5& $ \{ \it{X}_{s} \} _{\it{s} \in \mathcal{S}}$  & Family & Family $ \it{X} $ of $\it{s}$ & a sort-indexed family of disjoint finite sets $ \it{X}_s $ of variables $\it{x}$ of sort $ \it{s} $\\
-6& $\left[ \it{b} / \it{x}\right] \it{a}$ & Substitution & Substitute $\it{b}$ for $\it{x}$ in $\it{a}$ & Substitute  $\it{b}$ for $\it{x}$ in $\it{a}$ \\
-7& $ \it{x}_1, ... ,\it{x}_{\it{n}}.\it{a} $ & Abstractor & Bind variables $\it{x_n}$ to expression $\it{a}$ & Bind variables $\it{x_n}$ to expression $\it{a}$ \\
-8& $ \overrightarrow{\it{x}} $ & X arrow & List of $\it{x}s$ & $ \it{x}_1, ... ,\it{x}_{\it{n}} $ \\
-8& $ \rho : \overrightarrow{\it{x}} \leftrightarrow \overrightarrow{\it{x}}'$ & Fresh renaming & Freshen $ \it{x} $ using renaming $ \rho $ & A bijection between $ \overrightarrow{\it{x}} $ and $ \overrightarrow{\it{x}}' $ where $ \overrightarrow{\it{x}}'$ is fresh.
+\title{Cheat Sheet for PFPL}
+\maketitle
+\subsection*{I. Judgements and Rules}
+\subsubsection*{1 Abstract Syntax}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+1& 5& $\mathcal{P}$ & Script P & Proposition & Something to be proved \\
+2& 5& $\mathcal{P}(\it{a})$ & Script P of $\it{a}$ & Proposition about tree $\it{a}$ & Something to be proved about AST $\it{a}$ \\
+3& 5& $\mathcal{O}$ & Script O & Operator & An operator that can be used in an AST \\
+4& 5& $\mathcal{O}(\it{a})$ & Script O of $\it{a}$ & Operator of arity $\it{a}$ & An operator of a given arity \\
+5& 5& $\mathcal{X}_{\it{s}}$ & Script X sub s & Variables $\it{x}$ of sort $\it{s}$ & Variables $\it{x}$ of sort $\it{s}$ \\
+6& 5& $\it{S} $ & S & A set of sorts & A set of sorts \\
+7& 5& $ \{ \it{X}_{s} \} _{\it{s} \in \mathcal{S}}$  & Family & Family $ \it{X} $ of $\it{s}$ & A sort-indexed family of disjoint finite sets $ \it{X}_s $ of variables $\it{x}$ of sort $ \it{s} $\\
+8& 6& $\left[ \it{b} / \it{x}\right] \it{a}$ & Substitution & Substitute $\it{b}$ for $\it{x}$ in $\it{a}$ & Substitute  $\it{b}$ for $\it{x}$ in $\it{a}$ \\
+9& 7& $ \it{x}_1, ... ,\it{x}_{\it{n}}.\it{a} $ & Abstractor & Bind variables $\it{x_n}$ to expression $\it{a}$ & Bind variables $\it{x_n}$ to expression $\it{a}$ \\
+10& 8& $ \overrightarrow{\it{x}} $ & X arrow & List of $\it{x}s$ & $ \it{x}_1, ... ,\it{x}_{\it{n}} $ \\
+11& 8& $ \rho : \overrightarrow{\it{x}} \leftrightarrow \overrightarrow{\it{x}}'$ & Fresh renaming & Freshen $ \it{x} $ using renaming $ \rho $ & A bijection between $ \overrightarrow{\it{x}} $ and $ \overrightarrow{\it{x}}' $ where $ \overrightarrow{\it{x}}'$ is fresh.
 \\
-8& $\widehat{\rho}_{\it{i}} (a_{\it{i}})$ & Rho hat sub i & Rename result & The result of applying the renaming $ \rho_ {\it{i}} $ to $ \it{a}_{\it{i}} $ \\
-8& $x =_\alpha y$ & Equal alpha & $ \it{\alpha}$-$\it{equivalence} $ & Trees x and y equal up to renaming \\
-9& $x \overset{\Delta}{=} y$ & Delta equals & Replacement & Replace expression x with expression y \\
-13& $\tau$ type& Type & Type $\tau$ & Judgement that $\tau$ is a type \\
-13& $\it{e} : \tau$ & Colon &  $\it{e}$ is of type $\tau$ & Judgement that expression $\it{e}$ is of type $\tau$ \\
-13& $\it{e} \Downarrow \it{v}$ & Down arrow &  $\it{e}$ has value $\it{v} $ & Judgement that expression $\it{e}$ has value $\it{v} $\\
-14& $\infer {\it{J}} {\it{J}_{1}...\it{J}_{\it{k}}}$  & Surfboard & Infers & Judgements ${\it{J}_{1}...\it{J}_{\it{k}}}$ infer judgement ${\it{J}}$\\
-23 & ${\it{J}_{1}...\it{J}_{\it{k}}} \vdash_{\mathcal{R}} \mathcal{K}$ & Turnstile & Entails & Given $\mathcal{R}$ and $\it{J}$ infer $\mathcal{K}$\\
-23 & $\Gamma$ & Gamma & Judgements Gamma & A finite set of judgements \\
-23 & $\Delta$ & Delta & Judgements Delta & A finite set of judgements \\
-25 & $\Gamma \models_{\it{R}} \it{J}$ & Double turnstile & Admissible & $\vdash_{\it{R}} \Gamma$ implies $\vdash_{\it{R}} \it{J}$ \\
-28 & $\bigtriangledown$ & Down triangle & Generic derivation & Generic derivation \\
-41 & $\it{s} \mapsto \it{s'}$ & Bar arrow & Transistion  & State $\it{s}$ transitions to state $\it{s'}$ \\
+12& 8& $\widehat{\rho}_{\it{i}} (a_{\it{i}})$ & Rho hat sub i & Rename result & The result of applying the renaming $ \rho_ {\it{i}} $ to $ \it{a}_{\it{i}} $ \\
+13& 8& $x =_\alpha y$ & Equal alpha & $ \it{\alpha}$-$\it{equivalence} $ & Trees x and y equal up to renaming \\
+14& 9& $x \overset{\Delta}{=} y$ & Delta equals & Replacement & Replace expression x with expression y \\
+\end{tabular}
 
-42 & $\it{s} \mapsto ^{*} \it{s'}$ & Bar arrow star & Iterated transistion  & State $\it{s}$ transitions to state $\it{s'}$ over more than zero transitions \\
+\subsubsection*{2 Inductive Definitions}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
 
-42 & $\it{s} \mapsto ^{n} \it{s'}$ & Bar arrow n & N times iterated transistion  & State $\it{s}$ transitions to state $\it{s'}$ over n transitions \\
+15& 13& $\tau$ type& Type & Type $\tau$ & Judgement that $\tau$ is a type \\
+16& 13& $\it{e} : \tau$ & Colon &  $\it{e}$ is of type $\tau$ & Judgement that expression $\it{e}$ is of type $\tau$ \\
+17& 13& $\it{e} \Downarrow \it{v}$ & Down arrow &  $\it{e}$ has value $\it{v} $ & Judgement that expression $\it{e}$ has value $\it{v} $\\
+18& 14& $\infer {\it{J}} {\it{J}_{1}...\it{J}_{\it{k}}}$  & Surfboard & Infers & Judgements ${\it{J}_{1}...\it{J}_{\it{k}}}$ infer judgement ${\it{J}}$\\
 
-44 & $\mathcal{E}$  & Script E & Expression context & Expression context \\
+\end{tabular}
 
-45 & $\circ $ & Circle & Hole & Placeholder to put an instruction \\
-46 & $ \it{e} \equiv \it{e}' $ & Equivalent & Definitional equivalence & $\it{e}$ is definitionally equivalent to $\it{e}'$ \\
+\subsubsection*{3 Hypothetical and General Judgements}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+19& 23 & ${\it{J}_{1}...\it{J}_{\it{k}}} \vdash_{\mathcal{R}} \mathcal{K}$ & Turnstile & Entails & Given $\mathcal{R}$ and $\it{J}$ infer $\mathcal{K}$\\
 
-58 & $\it{e}??$ & Wrong & E goes wrong & Expression $\it{e}$ goes wrong \\
+20& 23 & $\Gamma$ & Gamma & Judgements Gamma & A finite set of judgements \\
+21& 23 & $\Delta$ & Delta & Judgements Delta & A finite set of type judgements \\
+22& 25 & $\Gamma \models_{\it{R}} \it{J}$ & Double turnstile & Admissible & $\vdash_{\it{R}} \Gamma$ implies $\vdash_{\it{R}} \it{J}$ \\
+23& 28 & $\bigtriangledown$ & Down triangle & Generic derivation & Generic derivation \\
+\end{tabular}
 
-58 & $\it{e} \Downarrow ^{\it{k}}\it{v}$  & Downarrow k & E evaluates in k steps & Expression $ \it{e}$ evaluates to $\it{v}$ in $\it{k}$ steps\\
+\subsection*{II. Statics and Dynamics}
 
-166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
+\subsubsection*{4 Statics}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+24& 36 & $ \it{n} ::= \it{s} $ & Colon colon equals & The syntax of $\it{n}$ is $\it{s}$ & Specifies the syntax of $\it{n}$ \\
+25& 36 & $;$ & Semicolon & And & Separates arguments to expressionsin abstact notation\\
+
+\end{tabular}
+
+\subsubsection*{5 Dynamics}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+26& 41 & $\it{s} \longmapsto \it{s'}$ & Bar arrow & Transistion  & State $\it{s}$ transitions to state $\it{s'}$ \\
+
+27& 42 & $\it{s} \longmapsto ^{*} \it{s'}$ & Bar arrow star & Iterated transistion  & State $\it{s}$ transitions to state $\it{s'}$ over more than zero transitions \\
+
+28& 42 & $\it{s} \longmapsto ^{n} \it{s'}$ & Bar arrow n & N times iterated transistion  & State $\it{s}$ transitions to state $\it{s'}$ over n transitions \\
+
+29& 44 & $\mathcal{E}$  & Script E & Expression context & Expression context \\
+
+30& 45 & $\circ $ & Circle & Hole & Placeholder to put an instruction \\
+31& 46 & $ \it{e} \equiv \it{e}' $ & Equivalent & Definitional equivalence & $\it{e}$ is definitionally equivalent to $\it{e}'$ \\
+
+\end{tabular}
+
+\subsubsection*{6 Type Safety}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+32& 58 & $\it{e}??$ & Wrong & E goes wrong & Expression $\it{e}$ goes wrong \\
+
+\end{tabular}
+\subsubsection*{7 Evaluation Dynamics}
+
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+33& 58 & $\it{e} \Downarrow ^{\it{k}}\it{v}$  & Downarrow k & E evaluates in k steps & Expression $ \it{e}$ evaluates to $\it{v}$ in $\it{k}$ steps\\
+\end{tabular}
+
+\subsection*{III. Total Functions}
+\subsubsection*{8 Function Definitions and Values}
+
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+34& 63 & $\{\it{f}\}$ & Brace brackets & Function & Surround function $\it{f}$ in abstract notation \\
+
+35& 63 & $\it{f}.\it{e}$ & Dot & Dot & Introduces the scope $\it{e}$ of a function $\it{f}$ in abstract notation \\
+36& 64 & $\it{f}(\tau_1):\tau_2$ & Function & Function definition & A function taking an argument of type $\tau_1$ and returning a value of type $\tau_2$ \\
+
+37& 64 & $\mathcal{|[}\it{x/e/f}\mathcal{]|}\it{e'}$ & Script bracket & Function substitution & Function substitution \\
+
+38& 65 & $\tau_1 \to \tau_2$ & Right arrow & Maps to & A total function that maps elements of type $\tau_1$ to elements of type $\tau_2$ \\
+39& 65 & $\lambda $ & Lambda & Lambda & Abstraction \\
+\end{tabular}
+\subsubsection*{9 System T of Higher-Order Recursion}
+
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+40& 71 & $\hookrightarrow$ & Hook arrow & Select & Deconstructor selector \\
+41& 71 & $|$ & Bar & Either & A choice \\
+42& 71 & $\overline{\it{n}}$ & Overline & Church numbering & The Church numbering \\
+43& 76 & $\lceil n \rceil$ & Divided hat & G$\ddot{o}$del numbering & The G$\ddot{o}$del numbering \\
+\end{tabular}
+\subsection*{IV. Finite Data Types}
+\subsubsection*{10 Product Types}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+44& 81 & $<>$ & Angle brackets & Null tuple & Null tuple \\
+45& 81 & $<e_1,e_2>$ & Angle brackets & Ordered pair & Ordered pair \\
+46& 81 & $e.$l & Left & Left projection & Select left member of the ordered pair \\
+47& 81 & $e.$r & Right & Right projection & Select right member of the ordered pair \\
+\end{tabular}
+\subsubsection*{11 Sum Types}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+48& 87 & l.$e$ & Left & Left injection & Create sum type element using left type \\
+49& 87 & r.$e$ & Right & Right injection & Create sum type element using right type \\
+\end{tabular}
+\subsection*{VI. Infinite Data Types}
+\subsubsection*{14 Generic Programming}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+50& 121 & $t.\tau$ & Dot & Type operator & Bind $t$ to type $\tau$ \\
+\end{tabular}
+\subsubsection*{15 Inductive and Coinductive Types}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+51& 133 & $ \cong $ & Tilde equal & Isomorphism & Isomorphism \\
+\end{tabular}
+\subsection*{VII. Variable Types}
+\subsubsection*{17 Abstract Types}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+52 & 149 & $\exists(t.\tau)$ & Exists & Interface & Defines an interface \\
+53 & 153 & $\forall(t.\tau\longrightarrow\tau_2)$ & Forall & Universal type & Defines universal type \\
+\end{tabular}
+
+\subsubsection*{18 Higher Kinds}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+54& 157 & $::$ & Colon colon & Kind type constructor & Maps types to types \\
+\end{tabular}
+\subsection*{VIII. Partiality and Recursive Types}
+\subsubsection*{19 System PCF of Recursive Functions}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+55& 166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
+56& 166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
+57& 167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
+\end{tabular}
+
+\subsubsection*{20 System FPC of Recursive Types}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+58& 177 & $\_$ & Underscore & Underscore & Unfree variable \\
+\end{tabular}
+\subsection*{IX. Dynamic Types}
+\subsubsection*{21 The Untyped $\lambda$-Calculus}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+59& 185 & $\Lambda$ & Lambda & Lambda calculus & The lambda calculus \\
+60& 188 & Y & Y & Y Combinator & The Y combinator \\
+61& 190 & $x^{\dagger}$ & Superscript cross & Superscript cross & Language isomorphism \\
+
 \end{tabular}

### 2016-03-15 pfpl/cheatsheet.tex
Back to desktop
Fix title and quantifiers

@@
 
-37& 64 & $\mathcal{|[}\it{x/e/f}\mathcal{]|}\it{e'}$ & Script bracket & Function substitution & Function substitution \\
+37& 64 &  $|[x/e/f]|e'$ & Script bracket & Function substitution & Function substitution \\
 
@@
 p{.22\textwidth} p{.32\textwidth}}
-52 & 149 & $\exists(t.\tau)$ & Exists & Interface & Defines an interface \\
-53 & 153 & $\forall(t.\tau\longrightarrow\tau_2)$ & Forall & Universal type & Defines universal type \\
+N & P & Expression & Name & Say & Meaning \\ \\
+52 & 149 & $\exists(t.\tau)$ & Existential quantifier & Exists & Defines an interface \\
+53 & 153 & $\forall(t.\tau\longrightarrow\tau_2)$ & Universal quantifier & For all & Defines universal type \\
 \end{tabular}

### 2016-05-13 pfpl/cheatsheet.tex
Corrected syntax for [[x.e/f]] p64
Also, better approximation of the double square brackets
Update cheat sheet

--- 2016-03-09 pfpl/cheatsheet.tex
@@
 
-37& 64 & $\mathcal{|[}\it{x/e/f}\mathcal{]|}\it{e'}$ & Script bracket & Function substitution & Function substitution \\
+37& 64 &  $[\![x.e/f]\!]e'$ & Script bracket & Function substitution & Function substitution \\
 
@@
 
-40& 71 & $\hookrightarrow$ & Hook arrow & Select & Deconstructor selector \\
+40& 71 & $\hookrightarrow$ & Hook arrow & Select & Selector (used in System T recursion, sum types, and product types)\\
 41& 71 & $|$ & Bar & Either & A choice \\
@@
 49& 87 & r.$e$ & Right & Right injection & Create sum type element using right type \\
+50& 93 & $\triangleq$ & Delta equals & Delta equals & Replacement \\
 \end{tabular}
+
 \subsection*{VI. Infinite Data Types}
@@
 
-50& 121 & $t.\tau$ & Dot & Type operator & Bind $t$ to type $\tau$ \\
+51& 121 & $t.\tau$ & Dot & Type operator & Bind $t$ to type $\tau$ \\
 \end{tabular}
@@
 
-51& 133 & $ \cong $ & Tilde equal & Isomorphism & Isomorphism \\
+52& 133 & $ \cong $ & Tilde equal & Isomorphism & Isomorphism \\
 \end{tabular}
@@
 p{.22\textwidth} p{.32\textwidth}}
-52 & 149 & $\exists(t.\tau)$ & Exists & Interface & Defines an interface \\
-53 & 153 & $\forall(t.\tau\longrightarrow\tau_2)$ & Forall & Universal type & Defines universal type \\
+N & P & Expression & Name & Say & Meaning \\ \\
+53 & 149 & $\exists(t.\tau)$ & Existential quantifier & Exists & Defines an interface \\
+54 & 153 & $\forall(t.\tau\longrightarrow\tau_2)$ & Universal quantifier & For all & Defines universal type \\
 \end{tabular}
@@
 
-54& 157 & $::$ & Colon colon & Kind type constructor & Maps types to types \\
+55& 157 & $::$ & Colon colon & Kind type constructor & Maps types to types \\
 \end{tabular}
@@
 
-55& 166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
-56& 166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
-57& 167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
+56& 166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
+57& 166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
+58& 167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
 \end{tabular}
@@
 
-58& 177 & $\_$ & Underscore & Underscore & Unfree variable \\
+59& 177 & $\_$ & Underscore & Underscore & Unfree variable \\
 \end{tabular}
@@
 
-59& 185 & $\Lambda$ & Lambda & Lambda calculus & The lambda calculus \\
-60& 188 & Y & Y & Y Combinator & The Y combinator \\
-61& 190 & $x^{\dagger}$ & Superscript cross & Superscript cross & Language isomorphism \\
+60& 185 & $\Lambda$ & Lambda & Lambda calculus & The lambda calculus \\
+61& 188 & Y & Y & Y Combinator & The Y combinator \\
+62& 190 & $x^{\dagger}$ & Superscript cross & Superscript cross & Language isomorphism \\
 
@@
 
+\subsection*{X. Subtyping}
+\subsubsection*{24 Structural Subtyping}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+63& 213 & $\tau'<:\tau$ & Subtype & $\tau'$ is a subtype of $\tau$ & $\tau'$ is a subtype of $\tau$ \\
+
+\end{tabular}
+
+\subsection*{XI. Dynamic Dispatch}
+\subsubsection*{27 Inheritance}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+64& 252 & $()^{\ddagger}$ & Isomorphism & Isomorphism & $()^{\ddagger}$ is a method isomorphism \\
+
+\end{tabular}
 \end{document}

### 2016-07-08 pfpl/draftcheatsheet.tex
Create draft version

--- 2016-05-13 pfpl/cheatsheet.tex
@@
 \end{tabular}
+
+\subsection*{XII. Control Flow}
+\subsubsection*{28 Control Stacks}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+65& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
+66& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
+67& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
+68& 258 & $\vartriangleright$ & Right triangle & Evaluate and push & Evaluate an expression and push the result into a stack frame \\
+69& 258 & $\vartriangleleft$ & Left triangle & Push & Push evaluated result into a frame\\
+70& 259 & $\vartriangleleft:\tau$ & Triangle colon & Push expression of type $\tau$ & Push expression of type $\tau$\\
+71& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
+72& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
+73& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\
+
+\end{tabular}
+
 \end{document}

### 2016-07-29 pfpl/draftcheatsheet.tex
Add more chapters

--- 2016-05-13 pfpl/cheatsheet.tex
@@
 \end{tabular}
+
+\subsection*{XII. Control Flow}
+\subsubsection*{28 Control Stacks}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+65& 257 & $k \vartriangleright e$ & Right triangle & Evaluation state & Evaluate $e$ on $k$ \\
+66& 257 & $k \vartriangleleft e$ & Left triangle & Return state & Evaluate $k$ on $e$\\
+67& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
+68& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
+69& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
+70& 259 & $k \vartriangleleft:\tau$ & Triangle colon & Stack $k$ expects value of type $\tau$ & Stack $k$ expects value of type $\tau$\\
+71& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
+72& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
+73& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\
+
+\end{tabular}
+\subsubsection*{29 Exceptions}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+74& 266 & $k \blacklozenge$ & Dark left triangle & Failed & Stack $k$ is in a failed state \\
+
+\end{tabular}
+
+\subsection*{XIII. Symbolic Data}
+\subsubsection*{31 Symbols}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+75 & 282 & $a \sim \tau$ & Tilde & Define $a$ & Define symbol $a$ as type $\tau$ \\
+76 & 282 & $\Sigma$ & Sigma & Symbol context & Set of symbol definitions \\
+77 & 284 & $'a$ & Quote & Symbol reference & Symbol reference \\
+\end{tabular}
+
+\subsubsection*{32 Fluid Binding}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+\end{tabular}
+
+\subsection*{XIV. Mutable State}
+\subsubsection*{34 Modernized Algol}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+\end{tabular}
+
 \end{document}

### 2016-08-05 pfpl/draftcheatsheet.tex
Bring up to date

@@
 N & P & Expression & Name & Say & Meaning \\ \\
+78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Tensor product &  Map symbol $a$ to expression $e$\\
+79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Tensor product &  Symbol $a$ is undefined\\
+80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Tensor product &  Symbol $a$ is indeterminate\\
 
@@
 
+81 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
 \end{tabular}

### 2016-08-10 pfpl/draftcheatsheet.tex
Bring up to chapter 34
Add assign and reference

@@
 
-81 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
+81& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
+82 & 308 & $*a$ & Star & Reference & Get the value of $a$\\
+82 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
+83 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
 \end{tabular}

### 2016-08-16 pfpl/cheatsheet.tex
Bring up to date

@@
 \end{tabular}
+
+\subsection*{XII. Control Flow}
+\subsubsection*{28 Control Stacks}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+65& 257 & $k \vartriangleright e$ & Right triangle & Evaluation state & Evaluate $e$ on $k$ \\
+66& 257 & $k \vartriangleleft e$ & Left triangle & Return state & Evaluate $k$ on $e$\\
+67& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
+68& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
+69& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
+70& 259 & $k \vartriangleleft:\tau$ & Triangle colon & Stack $k$ expects value of type $\tau$ & Stack $k$ expects value of type $\tau$\\
+71& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
+72& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
+73& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\
+
+\end{tabular}
+\subsubsection*{29 Exceptions}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+74& 266 & $k \blacklozenge$ & Dark left triangle & Failed & Stack $k$ is in a failed state \\
+
+\end{tabular}
+
+\subsection*{XIII. Symbolic Data}
+\subsubsection*{31 Symbols}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+75 & 282 & $a \sim \tau$ & Tilde & Define $a$ & Define symbol $a$ as type $\tau$ \\
+76 & 282 & $\Sigma$ & Sigma & Symbol context & Set of symbol definitions \\
+77 & 284 & $'a$ & Quote & Symbol reference & Symbol reference \\
+\end{tabular}
+
+\subsubsection*{32 Fluid Binding}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Extended by &  Map symbol $a$ to expression $e$\\
+79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Extended by &  Symbol $a$ is undefined\\
+80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Extended by &  Symbol $a$ is indeterminate\\
+
+\end{tabular}
+
+\subsection*{XIV. Mutable State}
+\subsubsection*{34 Modernized Algol}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+81& 308 & $x \leftarrow e ; m$ & Left arrow & Sequence & Execute command $m$ with $e$ substituted for $x$ \\
+82& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
+83 & 308 & $*a$ & Star & Reference & Get the value of $a$\\
+84 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
+85 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
+\end{tabular}
+
 \end{document}

### 2016-08-21 pfpl/draftcheatsheet.tex
Add new chapter

--- 2016-07-29 pfpl/draftcheatsheet.tex
@@
 N & P & Expression & Name & Say & Meaning \\ \\
+78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Extended by &  Map symbol $a$ to expression $e$\\
+79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Extended by &  Symbol $a$ is undefined\\
+80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Extended by &  Symbol $a$ is indeterminate\\
 
@@
 
+81& 308 & $x \leftarrow e ; m$ & Left arrow & Sequence & Execute command $m$ with $e$ substituted for $x$ \\
+82& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
+83 & 308 & $*a$ & Star & Contents & Get the value of $a$\\
+84 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
+85 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
+\end{tabular}
+
+\subsubsection*{35 Assignable References}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+86 & 320 & $ \& a $ & Ampersand & Reference & Reference to assignable \\
+
+\end{tabular}
+
+\subsubsection*{36 Lazy Evaluation}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+87 & 333 & $ \Longrightarrow $ & Long right arrow & Implies & Implication (low precedence) \\
+
 \end{tabular}

### 2016-10-21 pfpl/draftcheatsheet.tex
Chapter 39 not complete

@@
 N & P & Expression & Name & Say & Meaning \\ \\
-78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Extended by &  Map symbol $a$ to expression $e$\\
-79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Extended by &  Symbol $a$ is undefined\\
-80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Extended by &  Symbol $a$ is indeterminate\\
+78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Circle times & Extended by &  Map symbol $a$ to expression $e$\\
+79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Circle times & Extended by &  Symbol $a$ is undefined\\
+80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Circle times & Extended by &  Symbol $a$ is indeterminate\\
 
@@
 
+\subsection*{XV. Parallelism}
+\subsubsection*{37 Nested Parallelism}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+88& 344 & $c_1 \otimes c_2 $ & Circle times  & Parallel cost & Cost of executing in parallel \\
+88& 344 & $c_1 \oplus c_2 $ & Circle plus  & Sequential cost & Cost of executing in sequence \\
+90& 350 & $a_1 \hookrightarrow s_1 \otimes a_2 \hookrightarrow s_2$ & Circle times  & Parallel join & Join local states \\
+\end{tabular}
+
+\subsection*{XVI. Concurrency and Distribution}
+\subsubsection*{39 Process Calculus}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+91& 365 & $ \$ E$ & Dollar  & Synchronize & Synchronize parallel processes \\
+92& 365 & $E_1 + E_2 $ & Plus  & Choice & Pick one of 2 expressions \\
+93& 365 & $?a;P$ & Query  & Query & Query a channel \\
+94& 365 & $!a;P$ & Bang  & Signal & Signal a channel \\
+95 & 367 & $ P_1 \otimes P_2 $  & Circle times & Composition & Compose 2 concurrent processes \\
+96 & 369 & $ *P $  & Star & Replication & Replicate process $P$ \\
+97 & 373 & $ ! a ( e ; P ) $  & Bang & Send & Send expression $e$ on channel $a$ to process $P$ \\
+98 & 373 & $ ? a ( x . P ) $  & Query & Receive & Receive expression $e$ on channel $a$ in process $P$ \\
+
+\end{tabular}
+
 \end{document}

### 2016-11-11 pfpl/draftcheatsheet.tex
Added @ (map)
Bring draft up to Chapter 41

@@
 95 & 367 & $ P_1 \otimes P_2 $  & Circle times & Composition & Compose 2 concurrent processes \\
-96 & 369 & $ *P $  & Star & Replication & Replicate process $P$ \\
-97 & 373 & $ ! a ( e ; P ) $  & Bang & Send & Send expression $e$ on channel $a$ to process $P$ \\
-98 & 373 & $ ? a ( x . P ) $  & Query & Receive & Receive expression $e$ on channel $a$ in process $P$ \\
+96 & 367 & $P \overset{\alpha}{\longmapsto} P' $ & Maps to & Steps & $P$ steps to $P'$ if action $\alpha$ is permissible \\
+97 & 369 & $ *P $  & Star & Replication & Replicate process $P$ \\
+98 & 370 & $ \nu a . P $ & Nu & New channel & Declare new channel $a$ in process $P$ \\
+99 & 371 & $P \overset{\alpha}{\underset{\Sigma}{\longmapsto}} P' $ & Maps to & Steps & $P$ steps to $P'$ if action $\alpha$ is permissible in context $\Sigma$ \\
+100 & 373 & $ ! a ( e ; P ) $  & Bang & Send & Send expression $e$ on channel $a$ to process $P$ \\
+101 & 373 & $ ? a ( x . P ) $  & Query & Receive & Receive expression $e$ on channel $a$ in process $P$ \\
+102 & 376 & $ \tau $ chan & Tau & Channel type & Channel of type $\tau$ \\
+103 & 376 & $ \& a $ & Ampersand & Channel reference & Reference to channel $a$ \\
+104 & 376 & $ !!(e_1;e_2;P) $ & Bang bang & Send & Send message on channel $e_1$  \\
+105 & 376 & $ ??(e;x.P) $ & Query query & Receive & Receive message on channel $e$  \\
+106 & 377 & $ @ $ & At & Map & Maps lambda expressions to PiC \\
+\end{tabular}
 
+\subsubsection*{40 Concurrent Algol}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+107& 382 & $ P_1 \otimes P_2 $ & Circle times  & Concurrent & Run processes $P_1$ and $P_2$ concurrently \\
+108 & 382 & $ \nu a ~\tau . p $ & Nu & New channel & Create a new chanell \\
+109 & 383 & $ m \overset{\alpha}{\underset{\Sigma}{\Rightarrow}} \nu \Sigma ' \{ m' \otimes p'\} $ & Fat right arrow & Transitions & Command $m$ transitions to command $m'$ while creating new channels $\Sigma$  and
+new processes $p'$ . The action $\alpha$ specifies the interactions of which $m$ is capable when executed. \\
+\end{tabular}
+
+\subsubsection*{41 Distributed Algol}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+110 & 392 & $ a~\tau @ w $ & Tilde  & Declare & $a$ is a channel at site $w$ carrying payloads of type $\tau$ \\
 \end{tabular}

### 2016-12-02 pfpl/draftcheatsheet.tex
Add application from chapter 18 reunumber Add Chapter 43

--- 2016-08-21 pfpl/draftcheatsheet.tex
@@
 55& 157 & $::$ & Colon colon & Kind type constructor & Maps types to types \\
+56 & 158 & $e_1[e_2] $ & Bracket & Application & Apply (call) function \\
 \end{tabular}
@@
 
-56& 166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
-57& 166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
-58& 167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
+57& 166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
+58& 166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
+59& 167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
 \end{tabular}
@@
 
-59& 177 & $\_$ & Underscore & Underscore & Unfree variable \\
+60& 177 & $\_$ & Underscore & Underscore & Unfree variable \\
 \end{tabular}
@@
 
-60& 185 & $\Lambda$ & Lambda & Lambda calculus & The lambda calculus \\
-61& 188 & Y & Y & Y Combinator & The Y combinator \\
-62& 190 & $x^{\dagger}$ & Superscript cross & Superscript cross & Language isomorphism \\
+61& 185 & $\Lambda$ & Lambda & Lambda calculus & The lambda calculus \\
+62& 188 & Y & Y & Y Combinator & The Y combinator \\
+63& 190 & $x^{\dagger}$ & Superscript cross & Superscript cross & Language isomorphism \\
 
@@
 
-63& 213 & $\tau'<:\tau$ & Subtype & $\tau'$ is a subtype of $\tau$ & $\tau'$ is a subtype of $\tau$ \\
+64& 213 & $\tau'<:\tau$ & Subtype & $\tau'$ is a subtype of $\tau$ & $\tau'$ is a subtype of $\tau$ \\
 
@@
 
-64& 252 & $()^{\ddagger}$ & Isomorphism & Isomorphism & $()^{\ddagger}$ is a method isomorphism \\
+65& 252 & $()^{\ddagger}$ & Isomorphism & Isomorphism & $()^{\ddagger}$ is a method isomorphism \\
 
@@
 
-65& 257 & $k \vartriangleright e$ & Right triangle & Evaluation state & Evaluate $e$ on $k$ \\
-66& 257 & $k \vartriangleleft e$ & Left triangle & Return state & Evaluate $k$ on $e$\\
-67& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
-68& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
-69& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
-70& 259 & $k \vartriangleleft:\tau$ & Triangle colon & Stack $k$ expects value of type $\tau$ & Stack $k$ expects value of type $\tau$\\
-71& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
-72& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
-73& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\
+66& 257 & $k \vartriangleright e$ & Right triangle & Evaluation state & Evaluate $e$ on $k$ \\
+67& 257 & $k \vartriangleleft e$ & Left triangle & Return state & Evaluate $k$ on $e$\\
+68& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
+69& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
+70& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
+71& 259 & $k \vartriangleleft:\tau$ & Triangle colon & Stack $k$ expects value of type $\tau$ & Stack $k$ expects value of type $\tau$\\
+72& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
+73& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
+74& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\
 
@@
 
-74& 266 & $k \blacklozenge$ & Dark left triangle & Failed & Stack $k$ is in a failed state \\
+75& 266 & $k \blacklozenge$ & Dark left triangle & Failed & Stack $k$ is in a failed state \\
 
@@
 
-75 & 282 & $a \sim \tau$ & Tilde & Define $a$ & Define symbol $a$ as type $\tau$ \\
-76 & 282 & $\Sigma$ & Sigma & Symbol context & Set of symbol definitions \\
-77 & 284 & $'a$ & Quote & Symbol reference & Symbol reference \\
+76 & 282 & $a \sim \tau$ & Tilde & Define $a$ & Define symbol $a$ as type $\tau$ \\
+77 & 282 & $\Sigma$ & Sigma & Symbol context & Set of symbol definitions \\
+78 & 284 & $'a$ & Quote & Symbol reference & Symbol reference \\
 \end{tabular}
@@
 N & P & Expression & Name & Say & Meaning \\ \\
-78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Extended by &  Map symbol $a$ to expression $e$\\
-79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Extended by &  Symbol $a$ is undefined\\
-80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Extended by &  Symbol $a$ is indeterminate\\
+79 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Circle times & Extended by &  Map symbol $a$ to expression $e$\\
+80 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Circle times & Extended by &  Symbol $a$ is undefined\\
+81 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Circle times & Extended by &  Symbol $a$ is indeterminate\\
 
@@
 
-81& 308 & $x \leftarrow e ; m$ & Left arrow & Sequence & Execute command $m$ with $e$ substituted for $x$ \\
-82& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
-83 & 308 & $*a$ & Star & Contents & Get the value of $a$\\
-84 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
-85 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
+82& 308 & $x \leftarrow e ; m$ & Left arrow & Sequence & Execute command $m$ with $e$ substituted for $x$ \\
+83& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
+84 & 308 & $*a$ & Star & Contents & Get the value of $a$\\
+85 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
+86 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
 \end{tabular}
@@
 
-86 & 320 & $ \& a $ & Ampersand & Reference & Reference to assignable \\
+87 & 320 & $ \& a $ & Ampersand & Reference & Reference to assignable \\
 
@@
 
-87 & 333 & $ \Longrightarrow $ & Long right arrow & Implies & Implication (low precedence) \\
+88 & 333 & $ \Longrightarrow $ & Long right arrow & Implies & Implication (low precedence) \\
+
+\end{tabular}
+
+\subsection*{XV. Parallelism}
+\subsubsection*{37 Nested Parallelism}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+89& 344 & $c_1 \otimes c_2 $ & Circle times  & Parallel cost & Cost of executing in parallel \\
+90& 344 & $c_1 \oplus c_2 $ & Circle plus  & Sequential cost & Cost of executing in sequence \\
+91& 350 & $a_1 \hookrightarrow s_1 \otimes a_2 \hookrightarrow s_2$ & Circle times  & Parallel join & Join local states \\
+\end{tabular}
+
+\subsection*{XVI. Concurrency and Distribution}
+\subsubsection*{39 Process Calculus}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+92& 365 & $ \$ E$ & Dollar  & Synchronize & Synchronize parallel processes \\
+93& 365 & $E_1 + E_2 $ & Plus  & Choice & Pick one of 2 expressions \\
+94& 365 & $?a;P$ & Query  & Query & Query a channel \\
+95& 365 & $!a;P$ & Bang  & Signal & Signal a channel \\
+96 & 367 & $ P_1 \otimes P_2 $  & Circle times & Composition & Compose 2 concurrent processes \\
+97 & 367 & $P \overset{\alpha}{\longmapsto} P' $ & Maps to & Steps & $P$ steps to $P'$ if action $\alpha$ is permissible \\
+98 & 369 & $ *P $  & Star & Replication & Replicate process $P$ \\
+99 & 370 & $ \nu a . P $ & Nu & New channel & Declare new channel $a$ in process $P$ \\
+100 & 371 & $P \overset{\alpha}{\underset{\Sigma}{\longmapsto}} P' $ & Maps to & Steps & $P$ steps to $P'$ if action $\alpha$ is permissible in context $\Sigma$ \\
+101 & 373 & $ ! a ( e ; P ) $  & Bang & Send & Send expression $e$ on channel $a$ to process $P$ \\
+102 & 373 & $ ? a ( x . P ) $  & Query & Receive & Receive expression $e$ on channel $a$ in process $P$ \\
+103 & 376 & $ \tau $ chan & Tau & Channel type & Channel of type $\tau$ \\
+104 & 376 & $ \& a $ & Ampersand & Channel reference & Reference to channel $a$ \\
+105 & 376 & $ !!(e_1;e_2;P) $ & Bang bang & Send & Send message on channel $e_1$  \\
+106 & 376 & $ ??(e;x.P) $ & Query query & Receive & Receive message on channel $e$  \\
+107 & 377 & $ @ $ & At & Map & Maps lambda expressions to PiC \\
+\end{tabular}
+
+\subsubsection*{40 Concurrent Algol}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+108& 382 & $ P_1 \otimes P_2 $ & Circle times  & Concurrent & Run processes $P_1$ and $P_2$ concurrently \\
+109 & 382 & $ \nu a ~\tau . p $ & Nu & New channel & Create a new chanell \\
+110 & 383 & $ m \overset{\alpha}{\underset{\Sigma}{\Rightarrow}} \nu \Sigma ' \{ m' \otimes p'\} $ & Fat right arrow & Transitions & Command $m$ transitions to command $m'$ while creating new channels $\Sigma$  and
+new processes $p'$ . The action $\alpha$ specifies the interactions of which $m$ is capable when executed. \\
+\end{tabular}
+
+\subsubsection*{41 Distributed Algol}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+
+111 & 392 & $ a~\tau @ w $ & Tilde  & Declare & $a$ is a channel at site $w$ carrying payloads of type $\tau$ \\
+\end{tabular}
+
+\subsection*{XVII. Modularity}
+
+\subsubsection*{43 Singular Kinds and Subkinding}
+\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
+p{.22\textwidth} p{.32\textwidth}}
+N & P & Expression & Name & Say & Meaning \\ \\
+112 & 407 & $ c::k $ & Colon colon  & Define constructor &  Define constructor $c$ of kind $k$\\
+113 & 407 & $ k_1<::k_2 $ & Less than colon colon  & Subkind & Kind $k_1$ is a subkind of kind $k_2$\\
 
